On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-01-22 ms-suppinfo.Rnw
Remove abbreviations: RGR, AGR, WD, Hmax

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
\caption{Mean coefficient correlation r (+SD) between growth and traits measured by stage.  a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass (Seedmass) and e) Rate of CO2 assimilation (Aarea). The mean coefficients are weighted by sample size and established from 103 articles. Results shown here are from the ''ideal'' subset of data (for details see ``Material and Methods''), ``n'' indicates the number of correlations.}
\label{fig:figA4}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
\caption{Number of correlation extracted by traits, stage, and growth type (absolute vs relative, and measurement). a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea). Absolute growth rate (AGR) is on the left and relative growth rate (RGR) on the right of each plot. Results shown here are from the "ideal" subset of the data (for details see ``Material and Methods''). }
\label{fig:figA8}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA3.pdf}
\caption{Range of correlations (r) between
growth and traits reported in the literature. Plots show the coefficients of correlation (r)
between plant growth and a) Specific leaf area (SLA, n =
111), b) Wood density (WD, n = 64), c) Asymptotic
maximum height (Hmax, n = 23), d) Seed mass (Seedmass, n = 36 and
e) Rate of CO2 assimilation (Aarea, n = 24) reported from 103
articles. The x axis represents the article ID sorted by the average reported coefficient value r. Each bubble represents an r value, the diameter of the bubble is proportional to its weight in the meta-analysis (i.e. number of species). The colours correspond to the stage for which the r values have been recorded: red points correspond to adult stage, orange points to saplings, and blue points to seedlings. Results shown here are from the entire dataset (for details see ``Material and Methods''). }
\label{fig:figA3}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA7.pdf}
\caption{Funnel plots with filled in data based on the trim and fill method, showing transformed correlation coefficient z between growth and a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea). Note that in these plots the y axis is 1/number of species included in the correlation, not the replication for the correlation. The open points correspond to the estimated missing studies. The number of missing values is 4 for SLA,0 for WD, 0 for Hmax, 11 for seed mass and 0 for Aarea. Results shown here are from the entire dataset. Results with the "ideal" subset of data (for details see ``Material and Methods''), shown no missing values for all traits.}
\label{fig:figA7}
\end{figure}

@@

We developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available by searching exclusively on SLA and WD. This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English. Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}. This snapshot indicated that \Sexpr{round(fun_snapshot(Snapshot)$main.traits ,0)}\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD. And it was \Sexpr{round(fun_snapshot(Snapshot)$all.traits ,0)}\% of the literature that would be captured by SLA and WD for the total 19 traits. Thus we narrow our search to only cover these two main traits.

@@

\noindent\textbf{Results:} We observed high levels of heterogeneity for all traits (SLA :$I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["SLA"]], ~stageRGR)$Hlevel,0)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["SLA"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["SLA"]])$random[11],0)}\%, WD :$I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["WD"]], ~stage)$Hlevel,0)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["WD"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["WD"]])$random[11],0)}, Hmax: $I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["Hmax"]], ~stageRGR)$Hlevel,0)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["Hmax"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["Hmax"]])$random[11],0)}, seed mass: $I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["Seedmass"]], ~stage)$Hlevel,0)}\%, CI \Sexpr{round(fun_Heterogeneity.CI(GCi[["Seedmass"]])$random[7], 1)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["Seedmass"]])$random[11],1)}, Aarea: $I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["Aarea"]], ~stage)$Hlevel,1)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["Aarea"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["Aarea"]])$random[11],0)}) which suggests that the correlations coefficient r between growth and traits are not uniform across the range of studies investigated. This result suggested that a large part of the variance is not explained by sampling error.

For SLA, seed mass and Hmax, \Sexpr{round(fun_Heterogeneity.H(GCi[["SLA"]], ~stageRGR)$Hexplained,1)}\%, \Sexpr{round(fun_Heterogeneity.H(GCi[["Seedmass"]], ~stage)$Hexplained,1)}\% and \Sexpr{round(fun_Heterogeneity.H(GCi[["Hmax"]], ~stageRGR)$Hexplained, 0)}\% respectively of the total amount of heterogeneity were accounted for by including the ontogenetic stage as a moderator. For the other traits, the ontogenetic stage explained little or no part of the heterogeneity observed across studies ( WD: \Sexpr{round(fun_Heterogeneity.H(GCi[["WD"]], ~stage)$Hexplained, 0)}\% and Aarea: \Sexpr{round(fun_Heterogeneity.H(GCi[["Aarea"]], ~stage)$Hexplained, 1)}\% ). These results were consistent with our expectations about a shift in the relationship between growth and traits across plant size for SLA, seed mass and Hmax, and the absence of an effect for WD and Aarea (see Theoretical expectation section).

@@

The Rosenberg's Fail-safe (N) were \Sexpr{fun_fsn(GCi[["SLA"]])[2]}, \Sexpr{fun_fsn(GCi[["WD"]])[2]}, \Sexpr{fun_fsn(GCi[["Hmax"]])[2]}, \Sexpr{fun_fsn(GCi[["Seedmass"]])[2]}, \Sexpr{fun_fsn(GCi[["Aarea"]])[2]} for SLA, WD, Hmax, Seedmass, and Aarea, suggesting that a large number of studies with a mean correlation coefficient of 0 need to be added to the analysis before the cumulative correlation would become non-significant. N was greater than 5k+10 for all traits (120 $< N <$ 455).
These results suggest that the impact of publication bias is probably trivial in our meta-analyses.

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
\caption{Mean coefficient correlation r (+SD) between growth and traits measured by stage.  a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass (Seedmass) and e) Rate of CO2 assimilation (Aarea). The mean coefficients are weighted by sample size and established from 103 articles. Results shown here are from the ``ideal'' subset of data (for details see ``Material and Methods''), ``n'' indicates the number of correlations.}
\label{fig:figA4}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
\caption{Number of correlation extracted by traits, stage, and growth type (absolute vs relative, and measurement). a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea). Absolute growth rate (AGR) is on the left and relative growth rate (RGR) on the right of each plot. Results shown here are from the ``ideal'' subset of the data (for details see ``Material and Methods''). }
\label{fig:figA8}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA3.pdf}
\caption{Range of correlations (r) between
growth and traits reported in the literature. Plots show the coefficients of correlation (r)
between plant growth and a) Specific leaf area (SLA, n =
111), b) Wood density (WD, n = 64), c) Asymptotic
maximum height (Hmax, n = 23), d) Seed mass (n = 36) and
e) Rate of CO2 assimilation (Aarea, n = 24) reported from 103
articles. The x axis represents the article ID sorted by the average reported coefficient value r. Each bubble represents an r value, the diameter of the bubble is proportional to its weight in the meta-analysis (i.e. number of species). The colours correspond to the stage for which the r values have been recorded: red points correspond to adult stage, orange points to saplings, and blue points to seedlings. Results shown here are from the entire dataset (for details see ``Material and Methods''). }
\label{fig:figA3}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA7.pdf}
\caption{Funnel plots with filled in data based on the trim and fill method, showing transformed correlation coefficient z between growth and a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea). Note that in these plots the y axis is 1/number of species included in the correlation, not the replication for the correlation. The open points correspond to the estimated missing studies. The number of missing values is 4 for SLA, 0 for wood density, 0 for maximum height, 11 for seed mass and 0 for Aarea. Results shown here are from the entire dataset. Results with the "ideal" subset of data (for details see ``Material and Methods''), shown no missing values for all traits.}
\label{fig:figA7}
\end{figure}

@@

We developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available by searching exclusively on SLA and wood density. This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English. Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}. This snapshot indicated that \Sexpr{round(fun_snapshot(Snapshot)$main.traits ,0)}\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and wood density. And it was \Sexpr{round(fun_snapshot(Snapshot)$all.traits ,0)}\% of the literature that would be captured by SLA and wood density for the total 19 traits. Thus we narrow our search to only cover these two main traits.

@@

\noindent\textbf{Results:} We observed high levels of heterogeneity for all traits (SLA :$I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["SLA"]], ~stageRGR)$Hlevel,0)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["SLA"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["SLA"]])$random[11],0)}\%, wood density :$I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["WD"]], ~stage)$Hlevel,0)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["WD"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["WD"]])$random[11],0)}, maximum height: $I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["Hmax"]], ~stageRGR)$Hlevel,0)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["Hmax"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["Hmax"]])$random[11],0)}, seed mass: $I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["Seedmass"]], ~stage)$Hlevel,0)}\%, CI \Sexpr{round(fun_Heterogeneity.CI(GCi[["Seedmass"]])$random[7], 1)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["Seedmass"]])$random[11],1)}, Aarea: $I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["Aarea"]], ~stage)$Hlevel,1)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["Aarea"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["Aarea"]])$random[11],0)}) which suggests that the correlations coefficient r between growth and traits are not uniform across the range of studies investigated. This result suggested that a large part of the variance is not explained by sampling error.

For SLA, seed mass and maximum height, \Sexpr{round(fun_Heterogeneity.H(GCi[["SLA"]], ~stageRGR)$Hexplained,1)}\%, \Sexpr{round(fun_Heterogeneity.H(GCi[["Seedmass"]], ~stage)$Hexplained,1)}\% and \Sexpr{round(fun_Heterogeneity.H(GCi[["Hmax"]], ~stageRGR)$Hexplained, 0)}\% respectively of the total amount of heterogeneity were accounted for by including the ontogenetic stage as a moderator. For the other traits, the ontogenetic stage explained little or no part of the heterogeneity observed across studies (wood density: \Sexpr{round(fun_Heterogeneity.H(GCi[["WD"]], ~stage)$Hexplained, 0)}\% and Aarea: \Sexpr{round(fun_Heterogeneity.H(GCi[["Aarea"]], ~stage)$Hexplained, 1)}\% ). These results were consistent with our expectations about a shift in the relationship between growth and traits across plant size for SLA, seed mass and maximum height, and the absence of an effect for wood density and Aarea (see Theoretical expectation section).

@@

The Rosenberg's Fail-safe (N) were \Sexpr{fun_fsn(GCi[["SLA"]])[2]}, \Sexpr{fun_fsn(GCi[["WD"]])[2]}, \Sexpr{fun_fsn(GCi[["Hmax"]])[2]}, \Sexpr{fun_fsn(GCi[["Seedmass"]])[2]}, \Sexpr{fun_fsn(GCi[["Aarea"]])[2]} for SLA, wood density, maximum height, Seedmass, and Aarea, suggesting that a large number of studies with a mean correlation coefficient of 0 need to be added to the analysis before the cumulative correlation would become non-significant. N was greater than 5k+10 for all traits (120 $< N <$ 455).
These results suggest that the impact of publication bias is probably trivial in our meta-analyses.

### 2016-01-22 ms-suppinfo.tex
Remove abbreviations: RGR, AGR, WD, Hmax

We developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available by searching exclusively on SLA and WD. This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English. Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}. This snapshot indicated that 84\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD. And it was 70\% of the literature that would be captured by SLA and WD for the total 19 traits. Thus we narrow our search to only cover these two main traits.

@@

\noindent\textbf{Results:} We observed high levels of heterogeneity for all traits (SLA :$I^{2}$ 84\% CI: 80-91\%, WD :$I^{2}$ 63\% CI: 48-85, Hmax: $I^{2}$ 81\% CI: 70-93, seed mass: $I^{2}$ 90\%, CI 84.9-94.9, Aarea: $I^{2}$ 71.5\% CI: 42-86) which suggests that the correlations coefficient r between growth and traits are not uniform across the range of studies investigated. This result suggested that a large part of the variance is not explained by sampling error.

For SLA, seed mass and Hmax, 41\%, 20.2\% and 17\% respectively of the total amount of heterogeneity were accounted for by including the ontogenetic stage as a moderator. For the other traits, the ontogenetic stage explained little or no part of the heterogeneity observed across studies ( WD: 9\% and Aarea: 0.1\% ). These results were consistent with our expectations about a shift in the relationship between growth and traits across plant size for SLA, seed mass and Hmax, and the absence of an effect for WD and Aarea (see Theoretical expectation section).

@@

The Rosenberg's Fail-safe (N) were 10617, 3344, 1138, 2261, 643 for SLA, WD, Hmax, Seedmass, and Aarea, suggesting that a large number of studies with a mean correlation coefficient of 0 need to be added to the analysis before the cumulative correlation would become non-significant. N was greater than 5k+10 for all traits (120 $< N <$ 455).
These results suggest that the impact of publication bias is probably trivial in our meta-analyses.

>>>>

We developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available by searching exclusively on SLA and wood density. This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English. Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}. This snapshot indicated that 84\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and wood density. And it was 70\% of the literature that would be captured by SLA and wood density for the total 19 traits. Thus we narrow our search to only cover these two main traits.

@@

\noindent\textbf{Results:} We observed high levels of heterogeneity for all traits (SLA :$I^{2}$ 84\% CI: 80-91\%, wood density :$I^{2}$ 63\% CI: 48-85, maximum height: $I^{2}$ 81\% CI: 70-93, seed mass: $I^{2}$ 90\%, CI 84.9-94.9, Aarea: $I^{2}$ 71.5\% CI: 42-86) which suggests that the correlations coefficient r between growth and traits are not uniform across the range of studies investigated. This result suggested that a large part of the variance is not explained by sampling error.

For SLA, seed mass and maximum height, 41\%, 20.2\% and 17\% respectively of the total amount of heterogeneity were accounted for by including the ontogenetic stage as a moderator. For the other traits, the ontogenetic stage explained little or no part of the heterogeneity observed across studies (wood density: 9\% and Aarea: 0.1\% ). These results were consistent with our expectations about a shift in the relationship between growth and traits across plant size for SLA, seed mass and maximum height, and the absence of an effect for wood density and Aarea (see Theoretical expectation section).

@@

The Rosenberg's Fail-safe (N) were 10617, 3344, 1138, 2261, 643 for SLA, wood density, maximum height, Seedmass, and Aarea, suggesting that a large number of studies with a mean correlation coefficient of 0 need to be added to the analysis before the cumulative correlation would become non-significant. N was greater than 5k+10 for all traits (120 $< N <$ 455).
These results suggest that the impact of publication bias is probably trivial in our meta-analyses.
